Human Factors Influencing Visual Statistical Inference

### 2013-06-07 sociology_paper.tex
bootstrap explanation

\begin{figure}[hbtp] 
   \centering
   \begin{minipage}[c]{0.49\textwidth}
   \includegraphics[width=\textwidth]{tower.pdf}
   \end{minipage}
    \hfill
   \begin{minipage}[c]{0.45\textwidth}
   Freedom's Lighthouse Averages \\
      \includegraphics[width=\textwidth]{freedom-sim.pdf} 
   RealClearPolitics Averages\\
      \includegraphics[width=\textwidth]{rcp-sim.pdf} 
   \end{minipage}
   \caption{ \label{fig:tower} Electoral building plot of the results of the 2012 U.S. Presidential Election (left). On the right a histogram of 10,000 simulations from the same model. The $p$-value of observing results as extreme as in the  2012 U.S. election based on the bootstrap is 0.0533 (with Bootstrap standard error of 0.002).}
\end{figure}

>>>>

\begin{figure}[hbtp] 
   \centering
   \begin{minipage}[c]{0.49\textwidth}
   \includegraphics[width=\textwidth]{tower.pdf}
   \end{minipage}
    \hfill
   \begin{minipage}[c]{0.45\textwidth}
   Freedom's Lighthouse Averages \\
      \includegraphics[width=\textwidth]{freedom-sim.pdf} 
   RealClearPolitics Averages\\
      \includegraphics[width=\textwidth]{rcp-sim.pdf} 
   \end{minipage}
   \caption{ \label{fig:tower} Electoral building plot of the results of the 2012 U.S. Presidential Election (left). On the right two histograms of 10,000 simulations each based on polling averages from two different sources. For the histogram on the top, the $p$-value of observing results as extreme as  the  2012 U.S. election results based on the bootstrap is 0.0533 (with Bootstrap standard error of 0.002), making the election results almost significantly different from the polls. There is no indication of any inconsistency between polls and election results based on the bootstrap simulation below. The lineups are based on the top source. }
\end{figure}
